Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2015-04-11 Paper.tex
style
Full DAG creation

The nonce, $H_n$, must satisfy the relation:
\begin{equation}
\mathtt{PoW}(H, H_n, \mathbf{d})[0] = H_m \quad \wedge \quad \mathtt{PoW}(H, H_n, \mathbf{d})[1] \leqslant \frac{2^{256}}{H_d}
\end{equation}

With $\mathbf{d}$ being the current DAG, a large data set needed to compute the mixHash, and $\mathtt{PoW}$ is the proof-of-work function (see section \ref{ch:pow}): this evaluates to an array with the first item being the mixHash, to proof that a correct DAG has been used, and the second item being a pseudo-random number cryptographically dependent on $H$ and $\mathbf{d}$. Given an approximately uniform distribution in the range $[0, 2^{256})$, the expected time to find a solution is proportional to the difficulty, $H_d$.

@@

Thus we are able to define the block header validity function $V(H)$:
\begin{eqnarray}
V(H) & \equiv & \mathtt{PoW}(H, H_n, \mathbf{d})[0] = H_m \quad \wedge \\
& & \mathtt{PoW}(H, H_n, \mathbf{d})[1] \leqslant \frac{2^{256}}{H_d} \quad \wedge \\
& & H_d = D(H) \quad \wedge \\
& & H_g \le H_l  \quad \wedge \\
& & H_l < {P(H)_H}_l + \lfloor\frac{{P(H)_H}_l}{1024}\rfloor  \quad \wedge \\
& & H_l > {P(H)_H}_l - \lfloor\frac{{P(H)_H}_l}{1024}\rfloor  \quad \wedge \\
& & H_l \geqslant 125000  \quad \wedge \\
& & H_s > {P(H)_H}_s \quad \wedge \\
& & H_i = {P(H)_H}_i +1 \quad \wedge \\
& & \lVert H_x \rVert \le 1024
\end{eqnarray}

@@

@@

>>>>

The nonce, $H_n$, must satisfy the relation:
\begin{equation}
%\mathtt{PoW}(H, H_n) \dfrac{\leqslant}{den} \frac{2^{256}}{H_d}
\mathtt{PoW}(H, H_n) \leqslant \frac{2^{256}}{H_d}
\end{equation}

Where $\mathtt{PoW}$ is the proof-of-work function (see section \ref{ch:pow}): this evaluates to an pseudo-random number cryptographically dependent on the parameters $H$ and $H_n$. Given an approximately uniform distribution in the range $[0, 2^{256})$, the expected time to find a solution is proportional to the difficulty, $H_d$.

@@

Thus we are able to define the block header validity function $V(H)$:
\begin{eqnarray}
V(H) & \equiv & \mathtt{PoW}(H, H_n) \leqslant \frac{2^{256}}{H_d} \quad \wedge \\
& & H_d = D(H) \quad \wedge \\
& & H_g \le H_l  \quad \wedge \\
& & H_l < {P(H)_H}_l + \lfloor\frac{{P(H)_H}_l}{1024}\rfloor  \quad \wedge \\
& & H_l > {P(H)_H}_l - \lfloor\frac{{P(H)_H}_l}{1024}\rfloor  \quad \wedge \\
& & H_l \geqslant 125000  \quad \wedge \\
& & H_s > {P(H)_H}_s \quad \wedge \\
& & H_i = {P(H)_H}_i +1 \quad \wedge \\
& & \lVert H_x \rVert \le 1024
\end{eqnarray}

@@

\section{Ethash}\label{app:ethash}
\subsection{Definitions}
We employ the following definitions:

\begin{tabular*}{\columnwidth}[h]{lrl}
\toprule
Name & Value & Description \\
\midrule
$J_{wordbytes}$ & 4  & Bytes in word. \\
$J_{datasetinit}$ & $2^{30}$ & Bytes in dataset at genesis. \\
$J_{datasetgrowth}$ & $2^{23}$ & Dataset growth per epoch. \\
$J_{cacheinit}$ & $2^{24}$ & Cache growth per epoch. \\
$J_{cachegrowth}$ & $2^{17}$ & Cache growth per epoch. \\
$J_{cachemultiplier}$ & 1024 & Size of the dataset relative to the cache. \\
$J_{epoch}$ & 30000 & Blocks per epoch. \\
$J_{mixbytes}$ & 128 & mix length in bytes. \\
$J_{hashbytes}$ & 64 & Hash length in bytes. \\
$J_{datasetparents}$ & 256 & Number of parents of each dataset element. \\
$J_{cacherounds}$ & 3 & Number of parents of each dataset element. \\
$J_{accesses}$ & 64 & Number of accesses in hashimoto loop. \\
\bottomrule
\end{tabular*}

\subsection{Size of dataset and cache}
The size for Ethash's cache and dataset depend on the epoch, which depends on the block number.
\begin{equation}
 C_{epoch}(H_i) = \left\lfloor\frac{H_i}{J_{epoch}}\right\rfloor
\end{equation}
The size of the dataset growth by $J_{datasetgrowth}$, and the size of the cache by $J_{cachegrowth}$, every epoch. In order to avoid regularity leading to cyclic behavior, the size must be a prime number. Therefore the size is reduced by a multiple of $J_{mixbytes}$, for the dataset, and $J_{hashbytes}$ for the cache. 
Let $\mathbf{d}_{size} = \lVert \mathbf{d} \rVert$ be the size of the dataset. Which is calculated using
\begin{equation}
 \mathbf{d}_{size} = C_{prime}(J_{datasetinit} + J_{datasetgrowth} \cdot C_{epoch}, J_{mixbytes})
\end{equation}
The size of the cache, $\mathbf{c}_{size}$, is calculated using
\begin{equation}
 \mathbf{c}_{size} = C_{prime}(J_{cacheinit} + J_{cachegrowth} \cdot C_{epoch}, J_{hashbytes})
\end{equation}
\begin{equation}
 C_{prime}(x, y) = \begin{cases}
x & \text{if} \quad x \in \mathbb{P} \\
C_{prime}(x - y, y) & \text{otherwise}
\end{cases}
\end{equation}
\subsection{Dataset generation}
In order the generate the dataset we need the cache $\mathbf{c}$ which is an array of bytes. It depends on the cache size  $\mathbf{c}_{size}$ and the seed hash $\mathbf{s} \in \mathbb{B}_{32}$. 
\subsubsection{Seed hash}
The seed hash is different for every epoch. For the first epoch it is the Keccak-256 hash of a series of 32 bytes of zeros. For every other epoch it is always the Keccak-256 hash of the previous seed hash:
\begin{equation}
 \mathbf{s} = C_{seedhash}(H_i)
\end{equation}
\begin{equation}
 C_{seedhash}(H_i) = \begin{cases}
\texttt{KEC}(\mathbf{0}_{32}) & \text{if} \quad C_{epoch}(H_i) = 0 \quad  \\
\texttt{KEC}(C_{seedhash}(H_i - J_{epoch})) & \text{otherwise}
\end{cases}
\end{equation}
With $\mathbf{0}_{32}$ being 32 bytes of zeros.

\subsubsection{Cache}
The cache production process involves using the seed hash to first sequentially filling up $\mathbf{c}_{size}$ bytes of memory, then performing $J_{cacherounds}$ passes of \cite{lerner2014randmemohash} RandMemoHash algorithm:

The intial cache $\mathbf{c'}$, being an array of arrays of single bytes, will be constructed as follows:

We define the array $\mathbf{c}_{i}$, consisting of 64 single bytes,  as the $i$th element of the intial cache:
\begin{equation}
 \mathbf{c}_{i} = \begin{cases}
\texttt{KEC512}(\mathbf{s}) & \text{if} \quad i = 0 \quad  \\
\texttt{KEC512}(\mathbf{c}_{i-1}) & \text{otherwise}
\end{cases}
\end{equation}
Therefore $ \mathbf{c'}$ can be defined as 
\begin{equation}
 \mathbf{c'}[i] = \mathbf{c}_{i} \quad \forall \quad i < n
\end{equation}
\begin{equation}
 n = \left\lfloor\frac{\mathbf{c}_{size}}{J_{hashbytes}}\right\rfloor
\end{equation}
The cache is calculated by performing $J_{cacherounds}$ rounds of the RandMemoHash algorithm to the inital cache $\mathbf{c'}$:
\begin{equation}
 \mathbf{c} = E_{cacherounds}(\mathbf{c'}, J_{cacherounds})
\end{equation}
\begin{equation}
 E_{cacherounds}(\mathbf{x}, y) = \begin{cases}
\mathbf{x} & \text{if} \quad y = 0 \quad  \\
E_{rmh}(\mathbf{x}) & \text{if} \quad y = 1 \quad  \\
E_{cacherounds}(\mathbf{x}, y -1 ) & \text{otherwise}
\end{cases}
\end{equation}
Where a single round modifies each subset of the cache as follows:
\begin{equation}
 E_{rmh}(\mathbf{x}) = \lbrace E_{rmhSingle}(\mathbf{x}, 0), E_{rmhSingle}(\mathbf{x}, 1), ... , E_{rmhSingle}(\mathbf{x}, n) \rbrace
\end{equation}
\begin{equation}
  E_{rmhSingle}(\mathbf{x}, i) = \texttt{KEC512}(\mathbf{x}[(i - 1 + n) \mod n] \oplus \mathbf{x}[\mathbf{x}[i][0] \mod n) 
\end{equation}
\subsubsection{Full dataset calculation}
Essentially, we combine data from $J_{datasetparents}$ pseudorandomly selected cache nodes, and hash that to compute the dataset. The entire dataset is then generated by $\mathbf{d}_{size}$ items, each $J_{hashbytes}$ bytes in size:
\begin{equation}
 \mathbf{d}[i] = E_{datasetitem}(\mathbf{c}, i) \quad \forall \quad i < \left\lfloor\frac{\mathbf{d}_{size}}{J_{hashbytes}}\right\rfloor
\end{equation}
In order to calculate the single item we use an algorithm inspired by the FNV hash (\cite{FowlerNollVo1991FNVHash}) in some cases as a non-associative substitute for XOR.
\begin{equation}
 E_\text{\tiny FNV}(\mathbf{x}, \mathbf{y}) = (\mathbf{x} \cdot \mathrm{0x01000193} \oplus \mathbf{y}) \mod 2^{22}
\end{equation}
The single item of the dataset can now be calculated as:
\begin{equation}
 E_{datasetitem}(\mathbf{c}, i) = E_{parents}(\mathbf{c}, i, 0, \varnothing)
\end{equation}
\begin{equation}
  E_{parents}(\mathbf{c}, i, p, \mathbf{m}) = \begin{cases}
E_{parents}(\mathbf{c}, i, p +1, E'_{mix}) & \text{if} \quad p < J_{datasetparents} \\
E_{mix}(\mathbf{m}, \mathbf{c}, i, p) & \text{otherwise}
\end{cases}
\end{equation}
\begin{equation}
 E'_{mix}(\mathbf{m}, \mathbf{c}, i, p) = \begin{cases}
\texttt{KEC512}(\mathbf{c}[i \mod \mathbf{c}_{size}] \oplus i) & \text{if} \quad p = 0 \\
E_{mix}(\mathbf{m}, \mathbf{c}, i, p) & \text{otherwise}
\end{cases}
\end{equation}
\begin{equation}
 E_{mix}(\mathbf{m}, \mathbf{c}, i, p) = E_\text{\tiny FNV}(\mathbf{m}, \mathbf{c}[(E_\text{\tiny FNV}(i \oplus p), \mathbf{m}[ \lfloor J_{hashbytes} / J_{wordbytes} \rfloor]) \mod \mathbf{c}_{size})
\end{equation}

@@

C_\text{\tiny SSTORE}
